Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-10 main_paper.tex
update simulation table with HC3
The bootstrap estimator, naive estimator and robust estimator all use
HC3. Triangular kernel is used in this table, we can claim that other
kernels work similarly.

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method       & Bias    & SD    & RMSE  & CI Coverage (\%) & CI Length \\
    \midrule                                                     \\
    \multicolumn{7}{l}{Homoskedastic data with $\gamma = 0$ (Panel A)}  \\
    \midrule
    1 & Wild bootstrap & --0.014 & 0.067 & 0.069 & 0.917 & 0.237 \\ 
      & CCT            & --0.014 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
    2 & Wild bootstrap & --0.011 & 0.088 & 0.089 & 0.917 & 0.310 \\ 
      & CCT            & --0.011 & 0.088 & 0.089 & 0.935 & 0.351 \\
    3 & Wild bootstrap & --0.004 & 0.065 & 0.065 & 0.933 & 0.242 \\
      & CCT            & --0.004 & 0.065 & 0.065 & 0.938 & 0.251 \\ 
    \midrule                                                     \\
    \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
    \midrule
    1 & Wild bootstrap & --0.011 & 0.081 & 0.081 & 0.924 & 0.289 \\
      & CCT            & --0.011 & 0.081 & 0.081 & 0.931 & 0.301 \\ 
    2 & Wild bootstrap & --0.011 & 0.097 & 0.098 & 0.912 & 0.334 \\ 
      & CCT            & --0.011 & 0.097 & 0.097 & 0.931 & 0.379 \\
    3 & Wild bootstrap &   0.000 & 0.116 & 0.116 & 0.923 & 0.409 \\ 
      & CCT            &   0.000 & 0.116 & 0.116 & 0.935 & 0.432 \\
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

>>>>

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method       & Bias    & SD    & RMSE  & CI Coverage (\%) & CI Length \\
    \midrule                                                     \\
    \multicolumn{7}{l}{Homoskedastic data with $\gamma = 0$ (Panel A)}  \\
    \midrule
    1 & Wild bootstrap & --0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\ 
      & CCT            & --0.011 & 0.067 & 0.068 & 0.928 & 0.247 \\ 
      & Naive          & --0.037 & 0.041 & 0.055 & 0.835 & 0.155 \\ 
    2 & Wild bootstrap & --0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\ 
      & CCT            & --0.008 & 0.086 & 0.086 & 0.942 & 0.346 \\
      & Naive          & --0.145 & 0.065 & 0.159 & 0.353 & 0.241 \\
    3 & Wild bootstrap & --0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\ 
      & CCT            & --0.005 & 0.065 & 0.065 & 0.945 & 0.253 \\ 
      & Naive          &   0.034 & 0.051 & 0.061 & 0.862 & 0.191 \\ \\
    \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
    \midrule
    1 & Wild bootstrap & --0.010 & 0.080 & 0.081 & 0.934 & 0.301 \\
      & CCT            & --0.010 & 0.080 & 0.081 & 0.936 & 0.301 \\
      & Naive          & --0.035 & 0.050 & 0.061 & 0.863 & 0.185 \\ 
    2 & Wild bootstrap & --0.008 & 0.094 & 0.095 & 0.921 & 0.351 \\ 
      & CCT            & --0.008 & 0.094 & 0.095 & 0.924 & 0.366 \\
      & Naive          & --0.145 & 0.072 & 0.162 & 0.398 & 0.255 \\  
    3 & Wild bootstrap & --0.001 & 0.103 & 0.103 & 0.942 & 0.396 \\ 
      & CCT            & --0.001 & 0.103 & 0.103 & 0.942 & 0.395 \\ 
      & Naive          &   0.036 & 0.073 & 0.081 & 0.859 & 0.251 \\  
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}
